Four reasons your build is slow

### 2019-01-15 paper.tex
work on seconds 2 and 3

\documentclass[twocolumn,acmtog,10pt,review]{acmart}

\begin{document}
%\author{}
%\affiliation{}
%\author{}
%\affiliation{}

@@

An example of such a project with such a build is Facebook's zstd project \cite{}.  This project
has more than one long running CC command provide over 90\% of the running time of the build's
span.  Splitting the CC command into many parallel CC commands followed by a linking command
and then having the tool build a new graph presented a new span that was also dominated by
another long running CC command.

@@

Some projects may exhibit ample potential parallelism, but may be limited by systems that do not
have the resources to exploit said parallelism.  LLVM \cite{}

>>>>

\documentclass[twocolumn,sigplan,10pt,review]{acmart}
\title{Four reasons your build is slow}
\author{Sarah Spall}
\affiliation{Indiana University}
\author{Sam Tobin-Hochstadt}
\affiliation{Indiana University}

\begin{document}

\maketitle

@@

An example of a project with such a build is Facebook's zstd project \cite{}.  If we use our tool
to analyse the span of zstd's build, we see that the original span is dominated by a single call
to cc.
\begin{verbatim}
  cc -I../lib -I../lib/common -I../lib/compress -I../lib/dictBuilder -DXXH_NAMESPACE=ZSTD_ -I../lib/legacy -DZSTD_LEGACY_SUPPORT=5 -O3 -DBACKTRACE_ENABLE=0 ../lib/common/debug.c ../lib/common/entropy_common.c ../lib/common/error_private.c ../lib/common/fse_decompress.c ../lib/common/pool.c ../lib/common/threading.c ../lib/common/xxhash.c ../lib/common/zstd_common.c ../lib/compress/fse_compress.c ../lib/compress/hist.c ../lib/compress/huf_compress.c ../lib/compress/zstd_compress.c ../lib/compress/zstd_double_fast.c ../lib/compress/zstd_fast.c ../lib/compress/zstd_lazy.c ../lib/compress/zstd_ldm.c ../lib/compress/zstd_opt.c ../lib/compress/zstdmt_compress.c ../lib/decompress/huf_decompress.c ../lib/decompress/zstd_decompress.c ../lib/dictBuilder/cover.c ../lib/dictBuilder/divsufsort.c ../lib/dictBuilder/fastcover.c ../lib/dictBuilder/zdict.c ../lib/legacy/zstd_v05.c ../lib/legacy/zstd_v06.c ../lib/legacy/zstd_v07.c zstdcli.o fileio.o bench.o datagen.o dibio.o -o zstd
\end{verbatim}

If this call is no longer part of the span, we find that the new span is similarly dominated by
another single call to cc.

\begin{verbatim}
cc -I. -I./common -DXXH_NAMESPACE=ZSTD_ -I./legacy -DZSTD_LEGACY_SUPPORT=5 -O3 common/debug.c common/entropy_common.c common/error_private.c common/fse_decompress.c common/pool.c common/threading.c common/xxhash.c common/zstd_common.c compress/fse_compress.c compress/hist.c compress/huf_compress.c compress/zstd_compress.c compress/zstd_double_fast.c compress/zstd_fast.c compress/zstd_lazy.c compress/zstd_ldm.c compress/zstd_opt.c compress/zstdmt_compress.c decompress/huf_decompress.c decompress/zstd_decompress.c deprecated/zbuff_common.c deprecated/zbuff_compress.c deprecated/zbuff_decompress.c dictBuilder/cover.c dictBuilder/divsufsort.c dictBuilder/fastcover.c dictBuilder/zdict.c legacy/zstd_v05.c legacy/zstd_v06.c legacy/zstd_v07.c -shared -fPIC -fvisibility=hidden -Wl,-soname=libzstd.so.1 -o libzstd.so.1.3.7
\end{verbatim}

If their of these calls were members of the build's span, than our tool predicts the span would be
7.2 seconds rather than 39 seconds or 37 seconds (todo check that time).  To test this we manually
replaced the original calls with many calls that first compiled each file individually then later
linked them.  % todo fill in results.

@@

Some projects may exhibit ample potential parallelism, but even when run with more threads than
available parallelism, predicted parallelism may not be achieved.  LLVM \cite{} is the largest
project we analysed with a calculated work of approximately 12584 seconds, or 3.5 hours.  The
predicted span of LLVM is 305 seconds, or 5 minutes.  This gives LLVM a parallelism of about 41.
These calculations where made from a build of LLVM that was done not using strace.

A parallelism of 41 would lead one to believe that on a machine with 32 cores LLVM should be built
in parallel in about 5 minutes.  Our observations did not match this expectation.  When LLVM was
built with ``-j 32'' the observed speedup was slightly over 18; see chart \ref{}.  Using work and
span our tool can predict the potential speedup a build will experience using Brent's theorem
\cite{}.  The lower speedup bound is predicted using Brent's theorem, which specifies that for
P processors, \begin{math} T_P \leq T \end{math}

% say something about brent's theorem
% say something about why llvm doesnt achieve the predicted speedup
